---
title: "flat_first.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(dplyr)
library(ggplot2)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below
datafile <- system.file("nyc_squirrels_sample.csv", package = "my.package")
nyc_squirrels <- read.csv(datafile, encoding = "UTF-8")

datafile_2 <- system.file("unhcr-situations.csv", package = "my.package")

unhcr_situations <- read.csv(datafile_2, encoding = "UTF-8")

#nyc_squirrels
unhcr_situations
```


# The first function of the package: Calculate the median of a vector

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function-pop_type_destintation_countries}
#' Population Type by Destination Countries 
#'
#' @param country1 Country Selection
#' @inheritParams ggplot2::ggplot
#'
#' @return
#' Graph
#' @export
#'
#' @examples
pop_type_destintation_countries <- function(country1 = NULL,
                             country2 = NULL,
                             country3 = NULL,
                             country4 = NULL,
                             country5 = NULL){
  # Apply function
  df <- unhcr_situations |>
    select(Country, Individuals,Population.type)
  
  # Create a vector of countries to filter
  countries <- c(country1, country2, country3, country4, country5)
  countries <- countries[!is.null(countries)] # Remove NULL values
  countries <- tools::toTitleCase(countries) # Convert to Title case
  
  # Filter the data frame by the selected countries
  filtered_df <- df |>
    filter(Country %in% countries)
  
  box_p <- filtered_df |>
    ggplot2::ggplot(aes(x = Country,
                        y = Individuals,
                        fill = Population.type)) +
    geom_col()
    #geom_text(aes(label = Individuals))
    
  
  return(box_p)
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples}
# Example with your data set in "inst/"
datafile_2 <- system.file("unhcr-situations.csv", package = "my.package")
unhcr_situations <- read.csv(datafile_2, encoding = "UTF-8")

# Apply my function
pop_type_destintation_countries('Angola', 'zimbabwe', 'zambia')
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests-pop_type_destintation_countries}
test_that("pop_type_destintation_countries works", {
  expect_true(inherits(pop_type_destintation_countries, "function")) 
})
```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_first.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
